\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-27 manuscript.Rmd
Updates

---
title             : "Light Exposure Behavior Assessment"
shorttitle        : "Title"

@@

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
```

>>>>

---
title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
shorttitle        : "Title"

@@

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
r_refs("r-references.bib")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp) # devtools::install_github("cddesja/hemp")
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
```
